Envelope Estimation using Geometric Properties of a Discrete Real Signal

### 2021-05-07 Papers/01_Pulses_Envelope/PulsesEnvelope.tex
moving to elsevier template

$ E(t) $ represents the slow varying part of the wave, also known as the (temporal) envelope, modulator component, or amplitude modulation (AM) of $ W(t) $, while $ C(t) $ models its fast varying part, called throughout the literature as its (temporal) fine structure, carrier component, or frequency modulation (FM).

@@

We thus proceed to define a discrete curvature measure over the edges of a discrete curve. To that end we are going to apply the definition of smooth curvature as the rate of change of the unit tangent to a curve. This definition is convenient, since it is equivalent to that of the osculating circle \parencite{2016VasaMesh}.

One of those edges, a vector $ v_k \in \text{V} $, is singled out in Fig. \ref{fig:DiscreteCurvature}. $ v_k $ represents the net displacement of the envelope from the extrema $ P_{j} = (x_j, y_j) $ to $ P_{j+1} = (x_{j+1}, y_{j+1}) $. Since we don't yet know which points of P are part of the envelope, instead of assuming that the trajectory before $ P_{j} $ passes through $ P_{j-1} $, it is more prudent to assume that it can have passed anywhere in the line segment from points $ (x_j - (x_{j+1} - x_j), y_j - (y_{j+1} - y_j)) $ to $ (x_j - (x_{j+1} - x_j), y_j + (y_{j+1} - y_j)) $, the bold line segment before  $ v_k $ in Fig. \ref{fig:DiscreteCurvature}.

That is because all we can assume from $ v_k $ is that, in this current region of the envelope, it is able to a vertical displacement of $ v_{k,y} $ in the same time as it performs a horizontal displacement of $ v_{k,x} $;

@@

The radius of the circle equivalent to each $ v_k $ is defined in Eq. \ref{eq:Radius}. This equation has the desirable property that $ v_{k,y} \to 0 \implies v_{k,y} \to \infty $, that is, the radius tends to infinity when no vertical oscillation occurs, effectively turning the circle into a line. 
% It is also directly proportional to $ v_{k,x} $, making the radius larger the more the points are horizontally far from each other.

@@

For calculation purposes, however, this can cause a problem, as a zero could make its way into the denominator of a fraction; in the actual algorithm, the quantity calculated for each vector is the curvature itself, that is, the inverse of the radius. In this way, the problem is avoided, since $ v_{k,y} $ is guaranteed to be greater than zero. The average of curvatures is then inverted in order to obtain the average radius, as illustrated in Eq. \ref{eq:Curvature}.

>>>>

$ E(t) $ represents the slow varying part of the wave, also known as the (temporal) envelope, modulator component, or amplitude modulation (AM) of $ W(t) $, while $ C(t) $ models its fast varying part, called throughout the literature as its (temporal) fine structure, carrier wave, or frequency modulation (FM).

@@

We thus proceed to define a discrete curvature measure over the edges of a discrete curve. To that end we are going to apply the definition of smooth curvature as the rate of change of the unit tangent to a curve. This definition is convenient, since it is equivalent to that of the osculating circle \parencite{2016VasaMesh}, the value we are interested in finding.

One of those edges, in the form of the vector $ v_k \in \text{V} $, is singled out in Fig. \ref{fig:DiscreteCurvature}. $ v_k $ represents the net displacement of the envelope from the extrema $ P_{j} = (x_j, y_j) $ to $ P_{j+1} = (x_{j+1}, y_{j+1}) $. Since we don't yet know which points of P are part of the envelope, instead of assuming that the trajectory before $ P_{j} $ passes through $ P_{j-1} $, it is more prudent to assume that it can have passed anywhere in the line segment from points $ (x_j - (x_{j+1} - x_j), y_j - (y_{j+1} - y_j)) $ to $ (x_j - (x_{j+1} - x_j), y_j + (y_{j+1} - y_j)) $, the bold line segment before $ v_k $ in Fig. \ref{fig:DiscreteCurvature}.

That is because all we can safely assume from $ v_k $ is that, in the immediate vicinity of the vector, the envelope is capable of a vertical displacement of $ v_{k,y} $ in the same time as it performs a horizontal displacement of $ v_{k,x} $;

@@

The radius $ r_k $ of the circle equivalent to each $ v_k $ is defined in Eq. \ref{eq:Radius}. This equation has the desirable property that $ v_{k,y} \to 0 \implies v_{k,y} \to \infty $, that is, the radius tends to infinity when no vertical oscillation occurs, effectively turning the circle into a line.

The radius is also directly proportional to $ v_{k,x} $, making the radius larger the more the points are horizontally far from each other.

@@

For calculation purposes, however, this can pose a problem, as a zero could make its way into the denominator of a fraction; in the actual algorithm, the quantity calculated for each vector is the curvature itself, that is, the inverse of each radius $ r_k $. In this way, the problem is avoided, since $ v_{k,x} $ is guaranteed to be greater than zero. The average of curvatures is then inverted in order to obtain the average radius $ \overline{r} $, as illustrated in Eq. \ref{eq:Curvature}.
